Diagnoses and cell types

### 2025-09-04 analyses/infercnv-consensus-cell-type/exploratory-notebooks/reference-query-counts.Rmd
multiplexed sentence
update sep

      celltype_groups <- diagnosis_celltype_map |>
        dplyr::filter(diagnosis_group == broad_diagnosis) |>
        tidyr::separate_rows(celltype_groups, sep = ", ") |>
        dplyr::pull(celltype_groups)

@@

>>>>

      celltype_groups <- diagnosis_celltype_map |>
        dplyr::filter(diagnosis_group == broad_diagnosis) |>
        tidyr::separate_rows(celltype_groups, sep = ",") |>
        dplyr::pull(celltype_groups)

@@

Note that we are including multiplexed libraries from project `SCPCP000009` here as well; 11 libraries from that project from are eligible, most of which are multiplexed.
These libraries would effectively be using pooled references in `inferCNV`, since we did not demultiplex libraries.
